Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma

### 2013-03-01 Doc/Miccai2013/miccai2013.tex
ADD: global deformations finished
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@544 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\begin{figure}[htb]
  \centering
    \includegraphics[width=.95\textwidth]{forceEvolution.pdf}
  \caption{\label{fig-force}Evolution of forces during elastic warping.}
\end{figure}

\begin{figure}[htb]
  \centering
    \subfigure[]{\includegraphics[width=.32\textwidth]{gravity2.png}}
    \subfigure[]{\includegraphics[width=.32\textwidth]{registered.png}}
    \subfigure[]{\includegraphics[width=.32\textwidth]{distanceMap.png}}
  \caption{\label{fig-gravity}Vascularized liver under pure gravity with (red) and without (green) the capsule.}
\end{figure}

@@

\IP{Short overview, I'll put it together tomorrow morning and add some fancy images. I am not sure if we are going to mess up 
with gravity, it seems to me too much... We should rather focus only on this "registration-like" simulation (what about 
using term "elastic warping"??? and explain properly why we think it proves the capsule plays a role. My first shot:}

--we want to mimic a process takes place inside the pig such that it results in a natural deformation of the liver

--such a natural deformation happens when the position of the pig is changed from the flank to a supine position

--we performed a segmentation of both flank and supine and for some parts of the liver, displacements up to XXX\,cm  (I would say 3-4) 
were observed, which is enough given the size of the entire liver (18\,cm longest dimension)

--to induce the same deformation on the liver, we performed a process similar to deformation registration between the flank and supine 
data: we chosen a set of feature in flank and supine data such that each feature could be reliably located in both supine and flank 
data

--this set of features was extracted from the vascularization, since although the vascular tree is getting deformed together with the liver, 
the topology remains constant

--then we placed a linear spring to each feature location in the supine data, so it's attracted towards its flank position

--since the features were mapped to the elements via barycentric mapping, the entire model of the liver is being deformed, "elastically warped" from the 
supine to the flank position

--now the tricky part begins: we performed this process with models with and without the capsule; in each case we obtained 
a different resulting shape of liver

--additionally, we measured the forces needed to warp the liver in both cases: we obtained a difference summarized as.... ???

>>>>

\begin{figure}[htb]
  \centering
    \includegraphics[width=.95\textwidth]{forceEvolution.pdf}
  \caption{\label{f:forceEvol}Evolution of forces during elastic warping.}
\end{figure}

\begin{figure}[htb]
  \centering
    \subfigure[]{\includegraphics[width=.32\textwidth]{gravity2.png}}
    \subfigure[]{\includegraphics[width=.32\textwidth]{registered.png}}
    \subfigure[]{\includegraphics[width=.32\textwidth]{distanceMap.png}}
  \caption{\label{f:global}Vascularized liver under pure gravity with (red) and without (green) the capsule.}
\end{figure}

@@

The simulation with gravity was also used as a first demonstration of the global influence of the capsule. 
In Fig.~\ref{f:global}a, the models with capsule (red) and without (yellow) are depicted after being 
deformed due to the gravity, showing a significant difference between the two models.

In order to demonstrate the influence of the capsule on a real deformation of the liver, we 
performed a following protocol employing the supine and flank models built from the CT data. 
First, we performed a rigid registration of the two organs \wrt\ the root point of the hepatic vein. 
As shown in Fig.~\ref{f:global}b, the liver undergoes very large deformation when the body 
is turned from the supine to the flank position, exceeding 6\,cm for some parts of the organ. 
In order to induce similar deformation, we extracted feature pairs from the vascular system of the liver:
we selected points such as bifurcations which can be identified easily in each supine and flank 
model providing a set of correspondences. In the next stage, we used these correspondences as a non-homogeneous
boundary conditions (imposed via penalty term) in order to perform a deformable registration of the supine
model onto the flank data. During the registration, the response forces acting in the prescribed 
points were calculated. It is important to emphasize that the goal of the simulation was not 
to perform an accurate registration of the flank and supine data, however, the process was used 
as an example of real deformation that can be undertaken by the liver.

The registration process was performed with the vascularized model, however, the effect of the capsule was 
not considered. Once the static equilibrium was achieved, the effect of the capsule was gradually switched 
on, \ie\ the stiffness of the membrane was slowly increased from 0 to 8\,MPa. The force response in the 
prescribed points is depicted in Fig.~\ref{f:forceEvol} showing the change in the response as the effect
of the capsule is increased. At the same time, the shape of the deformed liver with capsule was compared 
to the model without capsule. A distance map is depicted in Fig.~\ref{f:global}c: in the red areas, the 
maximal difference of 1\,cm. We believe that this results confirms that the Glisson's capsule 
plays an important role in the mechanical response of the entire liver, \ie\ not only on the local, but 
also on the global level.
